Multi-channel Kondo model URG

### 2021-11-08 multi-channel-urg.tex
added one more argument for why the large J comparable to D situation is unreasonable

\textbf{\textit{The part of the problem that I have not yet figured out is the following: How do we argue for the same when \(J_0\) is not in the neighborhood of \(J_1^*\)? That is, if \(J_0\) is sufficiently large so that we cannot simpify the denominator. It is true that in order to compete with a thermodynamically large \(D_0\), the bare \(J_0\) will have to be extremely large, and it's possible that this does not even fall in the class of models we are studying.}}

>>>>

[\textit{The part of the problem that is not yet competely clear is the following: How do we argue for the same when \(J_0\) is not in the neighborhood of \(J_1^*\)? That is, if \(J_0\) is sufficiently large so that we cannot simpify the denominator. It is true that in order to compete with a thermodynamically large \(D_0\), the bare \(J_0\) will have to be extremely large, and it's possible that this does not even fall in the class of models we are studying. Also, if the Hamiltonian is to be extensive, \(J_0\) must scale as \(1/N\), because the conduction bath spin has two momentum space sums in product and each sum scales as \(N\). \(N\) is the number of particles. Hence, taking the limit of \(N \to \infty\) would mean \(J\) becoming smaller as compared to larger, so very large \(J_0\) seem unreasonable.}]
